Box 1 - TDT Curves

### 2023-09-23 ms/ms.qmd
Added some changes to text and reminders on what to write

@@

Models including phylogeny were better supported than models without phylogeny ($\Delta DIC$ = `r mcmcglmm_model_z_trans_nophylo$DIC - mcmcglmm_model_z_trans$DIC`), with all traits exhibiting a moderate to strong phylogenetic signal indicating evolutionary conservatism in heat tolerance (Phylogenetic $H^2$: $CT_{max}$ – `r posterior.mode(h2_ctmax)`, 95% CI: `r HPDinterval(h2_ctmax)[,"lower"]` to `r HPDinterval(h2_ctmax)[,"upper"]`; $z^{TDT}$ – `r posterior.mode(h2_z)`, 95% CI: `r HPDinterval(h2_z)[,"lower"]` to `r HPDinterval(h2_z)[,"upper"]`; CFLs – `r posterior.mode(h2_cfls)`, 95% CI: `r HPDinterval(h2_cfls)[,"lower"]` to `r HPDinterval(h2_cfls)[,"upper"]`). Nonetheless, there was within species variation ($I^2_{species}$: $CT_{max}$ – `r posterior.mode(spp_ctmax)`, 95% CI: `r HPDinterval(spp_ctmax)[,"lower"]` to `r HPDinterval(spp_ctmax)[,"upper"]`; $z^{TDT}$ – `r posterior.mode(spp_z)`, 95% CI: `r HPDinterval(spp_z)[,"lower"]` to `r HPDinterval(spp_z)[,"upper"]`; CFLs – `r posterior.mode(spp_cfls)`, 95% CI: `r HPDinterval(spp_cfls)[,"lower"]` to `r HPDinterval(spp_cfls)[,"upper"]`).

>>>>

$$
p_{i,k} \sim N\left(0, \right) \\

sp_{i,k} \sim N\left(0, \right) \\

e_{i,k} \sim N\left(0,  \right) \\
$$

@@

We obtained data for `r` species (). Models including phylogeny were better supported than models without phylogeny ($\Delta DIC$ = `r mcmcglmm_model_z_trans_nophylo$DIC - mcmcglmm_model_z_trans$DIC`), with all traits exhibiting a moderate to strong phylogenetic signal indicating evolutionary conservatism in heat tolerance (Phylogenetic $H^2$: $CT_{max}$ – `r posterior.mode(h2_ctmax)`, 95% CI: `r HPDinterval(h2_ctmax)[,"lower"]` to `r HPDinterval(h2_ctmax)[,"upper"]`; $z^{TDT}$ – `r posterior.mode(h2_z)`, 95% CI: `r HPDinterval(h2_z)[,"lower"]` to `r HPDinterval(h2_z)[,"upper"]`; CFLs – `r posterior.mode(h2_cfls)`, 95% CI: `r HPDinterval(h2_cfls)[,"lower"]` to `r HPDinterval(h2_cfls)[,"upper"]`). While the model also suggested that there was within species variation, missing data and lack of replicate species populations make conclusions premature ($I^2_{species}$: $CT_{max}$ – `r posterior.mode(spp_ctmax)`, 95% CI: `r HPDinterval(spp_ctmax)[,"lower"]` to `r HPDinterval(spp_ctmax)[,"upper"]`; $z^{TDT}$ – `r posterior.mode(spp_z)`, 95% CI: `r HPDinterval(spp_z)[,"lower"]` to `r HPDinterval(spp_z)[,"upper"]`; CFLs – `r posterior.mode(spp_cfls)`, 95% CI: `r HPDinterval(spp_cfls)[,"lower"]` to `r HPDinterval(spp_cfls)[,"upper"]`).
